Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Simplifies the use of the scale limits in the x axis

```{r item-plot-cov-out}
#| fig.cap: |
#|   Item plots in an oblique test space, with variances [2, 1.5]
plot_oblique +
  scale_x_continuous(
    limits       = c(-2, 4.2),
    breaks       = (0:4) - 2 / CORR_ARC_TAN,
    labels       = 0:4,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  )          +
  scale_color_manual(values = PALETTE)
```

>>>>

```{r item-plot-cov-out}
#| fig.cap: |
#|   Item plots in an oblique test space, with variances [2, 1.5]
plot_oblique    +
  xlim(-2, 4.2) +
  scale_color_manual(values = PALETTE)
```
